---
title: "2021 CCFRP Angler Survey Analysis"
author: "Cal Poly Team"
date: "September 2021"
output: 
  prettydoc::html_pretty:
    #toc: true
    #toc_depth: 4
    theme: tactile
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

```

```{r libraries}

library(tidyverse)
library(readxl)
library(patchwork)
library(here)

```


```{r read data, echo = F, eval = T}

## original data pulled 9/4
survey <- read_excel(here("Data", "CCFRP_angler_survey_2021_data.xlsx"))
survey <- survey[-(1:2),]



## updated dataset, pulled 9/13
survey2 <- read_excel(here("Data", "CCFRP_angler_survey_2021_data_2021-09-13.xlsx"))
survey2 <- survey2[-(1:2),]


```

### Marine Protected Areas

#### Questions 9 & 11

Before and after volunteering with CCFRP, what was your general opinion of the creation of MPAs in California?

```{r Q9 Q11, echo = F, eval = T}

## answer option list
beforeafter <- c('Positive', 'Somewhat positive', 'Neutral', 'Somewhat negative', 'Negative', 'No opinion')


## figure creation
Q9new <- survey %>% select(Q9) %>% drop_na() %>% count(Q9 = factor(Q9))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q9, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge", aes(fill = Q9, color = Q9))+
  scale_color_manual(values = c("#336633", "#336633", "#FFCC99", "#CC0000", "#CC0000", "#666666"))+
  scale_fill_manual(values = c("#336633", "#336633", "#FFCC99", "#CC0000", "#CC0000", "#666666"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,72)) +
  scale_x_discrete(labels = beforeafter) +
  labs(x = '\nBefore Volunteering with CCFRP', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")

Q11new <- survey %>% select(Q11) %>% drop_na() %>% count(Q11 = factor(Q11))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q11, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge", aes(fill = Q11, color = Q11))+
  scale_color_manual(values = c("#336633", "#336633", "#FFCC99", "#CC0000", "#CC0000", "#666666"))+
  scale_fill_manual(values = c("#336633", "#336633", "#FFCC99", "#CC0000", "#CC0000", "#666666"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,72)) +
  scale_x_discrete(labels = beforeafter) +
  labs(x = '\nAfter Volunteering with CCFRP', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")
```




```{r Q9 Q11 output, fig.height= 6, fig.width= 8, fig.align= "center", echo = F, eval = T}

Q9new/Q11new

#ba_plot <- Q9new/Q11new

#ggsave(here("Images","beforeafter.png"), plot = ba_plot , width = 8, height = 6, dpi = 1000)

```

```{r Q9 Q11 sample size, eval = F, echo = F}

## sample size

Q9n <- survey %>% select(Q9) %>% drop_na() %>% count(Q9 = factor(Q9))
sum(Q9n$n) ## 150 anglers

Q11n <- survey %>% select(Q11) %>% drop_na() %>% count(Q11= factor(Q11))
sum(Q11n$n) ## 150 anglers

```

### General

#### Questions 16 a-c

Have you experienced a difference in fishing in an MPA versus outside of an MPA?

* I catch more fish when fishing inside...

* I catch a greater diversity of fish species when fishing inside...

* I catch larger fish when I fish inside...

```{r Q16-Q18, echo = F, eval = T}

## answer option list
fishingarea <- c('MPAs', 'Open to Fishing', 'Don\'t Know', 'No Difference')

## figure creation
Q16new <- survey %>% select(Q16) %>% drop_na() %>% count(Q16 = factor(Q16))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q16, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge", fill = "#999999", color = "#333333", size = 1)+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,80)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nHigher Abundance', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")

Q17new <- survey %>% select(Q17) %>% drop_na() %>% count(Q17 = factor(Q17))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q17, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge", fill = "#999999", color = "#333333", size = 1)+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,80)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nGreater Diversity', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")

Q18new <- survey %>% select(Q18) %>% drop_na() %>% count(Q18 = factor(Q18))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q18, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge", fill = "#999999", color = "#333333", size = 1)+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,80)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nLarger Size', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")

```


```{r Q16-Q18 output, fig.height= 10, fig.width= 8, fig.align= "center", echo = F, eval = T}

Q16new/Q17new/Q18new

MPAREF_plot <- Q16new/Q17new/Q18new

# ggsave(here("Images","mpa_v_ref.png"), plot = MPAREF_plot , width = 8, height = 6, dpi = 1000)


```

```{r Q16-18 sample size, eval = F, echo = F}

## sample size 
Q16n <- survey %>% select(Q16) %>% drop_na() %>% count(Q16 = factor(Q16))
sum(Q16n$n) ## 107

Q17n <- survey %>% select(Q17) %>% drop_na() %>% count(Q17 = factor(Q17))
sum(Q17n$n) ## 107

Q18n <- survey %>% select(Q18) %>% drop_na() %>% count(Q18 = factor(Q18))
sum(Q18n$n) ## 107


```

#### Question 18

Hypothetically, how much would you be willing to pay for one day of catch and release fishing inside an MPA while not participating on a CCFRP trip?

```{r Q20, echo = F, eval= T}

money <- c('$0', '$1 - $20', '$21 - $50', '$51 - 100', '$101 - $500', '>$500')

Q20new <- survey %>% select(Q20) %>% drop_na() %>% count(Q20 = factor(Q20))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q20, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,80)) +
  scale_x_discrete(labels = money) +
  labs(x = '\nHow Much Would You Pay to Fish in an MPA?', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")

```


```{r Q20 output, fig.height= 6, fig.width= 10, fig.align= "center", echo = F, eval= T}

Q20new

```


```{r Q20 sample size, echo = F, eval = F}

## sample size 
Q20n <- survey %>% select(Q20) %>% drop_na() %>% count(Q20 = factor(Q20))
sum(Q20n$n) ## 145

```


### Natural Resource Conservation

#### Question 23

In your opinion, how well are California groundfish stocks managed? 

```{r Q26, echo = F, eval = T}

managed <- c('Very Well', 'Well', 'Adequately', 'Poorly', 'Very Poorly', 'Not Managed', 'Don\'t Know')


Q26new <- survey %>% select(Q26) %>% drop_na() %>% count(Q26 = factor(Q26))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q26, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,80)) +
  scale_x_discrete(labels = managed) +
  labs(x = '\nHow Well Managed are California Fisheries?', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")

```


```{r Q26 output, fig.height= 6, fig.width= 10, fig.align= "center", echo = F, eval = T}

Q26new

```

```{r Q26 sample size, echo = F, eval = F}

## sample size 
Q26n <- survey %>% select(Q26) %>% drop_na() %>% count(Q26 = factor(Q26))
sum(Q26n$n) ## 148

```

### Basic Demographics

#### Questions 28 - 31

```{r Q31-Q34, echo = F, eval = T}

## figure creation
Q31new <- survey2 %>% select(Q31) %>% drop_na() %>% count(Q31 = factor(Q31))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q31, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = c('Male', 'Female', 'Non-binary', 'Prefer not to state', 'Other')) +
  labs(x = '\nGender Identity', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")


Q32new <- survey %>% select(Q32) %>% drop_na() %>% count(Q32 = factor(Q32))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q32, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,40)) +
  scale_x_discrete(labels = c('18-24', '25-34', '35-44','45-54','55-64','65 and up')) +
  labs(x = '\nAge', y = '\nPercent') +
  theme_bw() +
  theme(panel.grid = element_blank(),
        legend.position = "none",
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))


Q33new <- survey %>% select(Q33) %>% drop_na() %>% count(Q33 = factor(Q33))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q33, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge", fill = "#3333FF", color = "#000066", size = 1)+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 3)+
  scale_y_continuous(limits = c(0,60)) +
  scale_x_discrete(labels = c('Less than \nhigh school degree', 'High school \ndegree', 'Associates degree \nor Tech school', 'Some college', 'College degree', 'Graduate degree')) +
  labs(x = '\nEducation', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")

Q34new <- survey %>% select(Q34) %>% drop_na() %>% count(Q34 = factor(Q34))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q34, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = 0.0,
            hjust = -0.7,
            size = 3)+
  scale_y_continuous(limits = c(0,25)) +
  scale_x_discrete(labels = c('<$25k', '$25-$35k', '$35-$50k', '$50-$75k', '$75-$100k', '$100-$150k', '$150-$200k', '>$200k', 'Decline to State')) +
  labs(x = '\nIncome', y = '\nPercent') +
  coord_flip()+
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none")

```

I identify as...

```{r Q31 output, fig.height= 6, fig.width= 10, fig.align= "center", echo = F, eval = T}

Q31new

```

What is your age?

```{r Q32 output, fig.height= 6, fig.width= 10, fig.align= "center", echo = F, eval = T}

Q32new

```

What is the highest level of education you have completed?

```{r Q33 output, fig.height= 6, fig.width= 10, fig.align= "center", echo = F, eval = T}

Q33new

```

Which of the following categories best describes your household’s total annual income before taxes in 2020? 

```{r Q34 output, fig.height= 6, fig.width= 10, fig.align= "center", echo = F, eval = T}

Q34new

```



```{r Q31-Q34 sample size, echo = F, eval = F}

## 
Q31n <- survey %>% select(Q31) %>% drop_na() %>% count(Q31 = factor(Q31))
sum(Q31n$n) ## 148

Q32n <- survey %>% select(Q32) %>% drop_na() %>% count(Q32 = factor(Q32))
sum(Q32n$n) ## 148


##
Q33n <- survey %>% select(Q33) %>% drop_na() %>% count(Q33 = factor(Q33))
sum(Q33n$n) ## 148


## annual income question
Q34n <- survey %>% select(Q34) %>% drop_na() %>% count(Q34 = factor(Q34))
sum(Q34n$n) ## 146

```




### For Snapshot Analysis

From this point forward, all graphs are set up the same way - Standard ggplot grey color, larger font size etc. These are the graphs that made it into the google doc.

**FONT SIZE**
To change the size of the percentages above bars, change the `size` argument in geom_text. To change the size of the axis title or text, change the 'size' argument inside of the 'theme' function --this should be the last function on the end of each ggplot.

**PLOT COLOR**
-For bars that are all one color: include a `fill` and `color` argument inside of geom_col(), but OUTSIDE of the aestheic function `aes()`. Assign a fill and color using hexidecimal ggplot colors. Examples are '#000666', #CC6600' which have to be in quotes. You can find all the colors here: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/. --SEE LINE 337 FOR EXAMPLE

-For bars that are different colors, assign the colors manually. Add a `fill` and `color` argument INSIDE of `aes()` inside of `geom_col()`. Then add two more functions to ggplot: `scale_fill_manual()` and `scale_color_manual()` with the designated colors inside. -- SEE LINE 76, 77, & 78 FOR EXAMPLE

**ORIENTATION**
To turn the bars horizonally, add the function `coord_flip()` to ggplot

```{r}

beforeafter2 <- c('Positive', 'Somewhat \npositive', 'Neutral', 'Somewhat \nnegative', 'Negative', 'No opinion')

ss9 <- survey2 %>% select(Q9) %>% drop_na() %>% count(Q9 = factor(Q9))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q9, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  #, aes(fill = Q9, color = Q9)
  #scale_color_manual(values = c("#336633", "#336633", "#FFCC99", "#CC0000", "#CC0000", "#666666"))+
  #scale_fill_manual(values = c("#336633", "#336633", "#FFCC99", "#CC0000", "#CC0000", "#666666"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = beforeafter2) +
  labs(x = '\nBefore Volunteering with CCFRP', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss11 <- survey2 %>% select(Q11) %>% drop_na() %>% count(Q11 = factor(Q11))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q11, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  # , aes(fill = Q11, color = Q11)
  # scale_color_manual(values = c("#336633", "#336633", "#FFCC99", "#CC0000", "#CC0000", "#666666"))+
  # scale_fill_manual(values = c("#336633", "#336633", "#FFCC99", "#CC0000", "#CC0000", "#666666"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = beforeafter2) +
  labs(x = '\nAfter Volunteering with CCFRP', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss9and11 <- ss9/ss11

#ggsave(here("Images","ss9_11.png"), plot = ss9and11 , width = 8, height = 6, dpi = 1000)



```


```{r}

ss16 <- survey2 %>% select(Q16) %>% drop_na() %>% count(Q16 = factor(Q16))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q16, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nHigher Abundance', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss17 <- survey2 %>% select(Q17) %>% drop_na() %>% count(Q17 = factor(Q17))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q17, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nGreater Diversity', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss18 <- survey2 %>% select(Q18) %>% drop_na() %>% count(Q18 = factor(Q18))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q18, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nLarger Size', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

mpa_ref <- ss16/ss17/ss18

##check samplesize

# ss16n <- survey2 %>% select(Q16) %>% drop_na() %>% count(Q16 = factor(Q16))
# sum(ss16n$Q16) ##141
# 
# ss17n <- survey2 %>% select(Q17) %>% drop_na() %>% count(Q17 = factor(Q17))
# sum(ss17n$n) ##141
# 
# ss18n <- survey2 %>% select(Q18) %>% drop_na() %>% count(Q18 = factor(Q18))
# sum(ss18n$n) ## 141

# ggsave(here("Images","ss16_18.png"), plot = mpa_ref , width = 8, height = 6, dpi = 1000)

```


```{r}

ss20 <- survey2 %>% select(Q20) %>% drop_na() %>% count(Q20 = factor(Q20))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q20, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,50)) +
  scale_x_discrete(labels = money) +
  labs(x = '\nHow Much Would You Pay to Fish in an MPA?', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

#ggsave(here("Images","ss20.png"), plot = ss20 , width = 8, height = 6, dpi = 1000)

#Q20n <- survey2 %>% select(Q20) %>% drop_na() %>% count(Q20 = factor(Q20))
#sum(Q20n$n)

```

```{r}

ss26 <- survey2 %>% select(Q26) %>% drop_na() %>% count(Q26 = factor(Q26))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q26, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,50)) +
  scale_x_discrete(labels = managed) +
  labs(x = '\nHow Well Managed are California Fisheries?', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

#ggsave(here("Images","ss26.png"), plot = ss26 , width = 8, height = 6, dpi = 1000)

# ss26n <- survey2 %>% select(Q26) %>% drop_na() %>% count(Q26 = factor(Q26))
# sum(ss26n$n)

```

```{r}

ss31 <- survey2 %>% select(Q31) %>% drop_na() %>% count(Q31 = factor(Q31))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q31, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = c('Male', 'Female', 'Non-binary', 'Prefer not to state', 'Other')) +
  labs(x = '\nGender Identity', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none",
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))


ss32 <- survey2 %>% select(Q32) %>% drop_na() %>% count(Q32 = factor(Q32))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q32, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,40)) +
  scale_x_discrete(labels = c('18-24', '25-34', '35-44','45-54','55-64','65 and up')) +
  labs(x = '\nAge', y = '\nPercent') +
  theme_bw() +
  theme(panel.grid = element_blank(),
        legend.position = "none",
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))


ss33 <- survey2 %>% select(Q33) %>% drop_na() %>% count(Q33 = factor(Q33))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q33, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,60)) +
  scale_x_discrete(labels = c('Less than \nhigh school degree', 'High school \ndegree', 'Associates degree \nor Tech school', 'Some college', 'College degree', 'Graduate degree')) +
  labs(x = '\nEducation', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none",
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss34 <- survey2 %>% select(Q34) %>% drop_na() %>% count(Q34 = factor(Q34))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = Q34, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,25)) +
  scale_x_discrete(labels = c('<$25k', '$25-\n$35k', '$35-\n$50k', '$50-\n$75k', '$75-\n$100k', '$100-\n$150k', '$150-\n$200k', '>$200k', 'Decline \nto State')) +
  labs(x = '\nIncome', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none",
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

#ggsave(here("Images","ss34.png"), plot = ss34 , width = 8, height = 6, dpi = 1000)

ss31n <- survey2 %>% select(Q31) %>% drop_na() %>% count(Q31 = factor(Q31))
sum(ss31n$n) ## 200

ss32n <- survey2 %>% select(Q32) %>% drop_na() %>% count(Q32 = factor(Q32))
sum(ss32n$n) ## 199


##
ss33n <- survey2 %>% select(Q33) %>% drop_na() %>% count(Q33 = factor(Q33))
sum(ss33n$n) ## 198

ss34n <- survey2 %>% select(Q34) %>% drop_na() %>% count(Q34 = factor(Q34))
sum(ss34n$n) ## 196

```

