---
title: "CCFRP Survey Basic Figures"
author: "E. Johnston, E. Brauer, G. Waltz, B. Ruttenberg, D. Wendt"
date: "12/2/2021"
output: 
 prettydoc::html_pretty:
    toc: TRUE
    toc_depth: 3
    theme: architect
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      warning = F,
                      message = F)

```

```{r packages}

library(tidyverse)    ## general
library(here)         ## calling data
library(knitr)        ## general
library(kableExtra)   ## for kable styling
library(patchwork)    ## for combining plots
library(ggsci)        ## for color mixer
library(lemon)        ## for brackets
library(ggpubr)       ## for combining plots & common legend
library(cowplot)      ## plotting images on graph
library(plotrix)      ## standard error function

```

```{r data and cleaning, echo = F}


survey_dat <- read_csv(here("Data", "2021-11-17_CCFRP_Angler_Survey_values_corr.csv"))

survey_dat <- survey_dat[-c(1:2),]
##297 responses

names(survey_dat) <- tolower(names(survey_dat))

survey_dat_clean <- survey_dat %>%
  filter(finished == 1,
         distributionchannel != "preview") 

survey_dat_clean <- survey_dat_clean %>%
  mutate(unanswered = rowSums(is.na(survey_dat_clean))) %>%
  ## to get rid of the responses where every single question was unanswered.
  filter(unanswered < 55) %>%
  mutate(q1 = as.numeric(q1))


```

## Section 2) Marine Protected Areas

### 9 & 11

**Before and After** volunteering with CCFRP, what was your general opinion of the creation of MPAs in California? My general opinion or MPA creation was ...

```{r beforeafter_eb setup, echo = F}

beforeafter <- c('Positive', 'Somewhat \npositive', 'Neutral', 'Somewhat \nnegative', 'Negative', 'No opinion')

ss9 <- survey_dat_clean %>% select(q9) %>% drop_na() %>% 
  count(q9 = factor(q9))%>% 
  mutate(pct9 = n/sum(n)*100,
         pct9 = round(pct9, digits = 0))

ss11 <- survey_dat_clean %>% select(q11) %>% drop_na() %>% 
  count(q11 = factor(q11)) %>%
  mutate(pct11 = n/sum(n)*100,
         pct11 = round(pct11, digits = 0))

ss911df <- data.frame(ss9$q9, ss9$pct9, ss11$q11, ss11$pct11) %>%
  pivot_longer(cols=c('ss9.pct9', 'ss11.pct11'), names_to='question', values_to="pct") %>%
  mutate(question=as.factor(question), ss9.q9 = as.factor(ss9.q9)) %>% select(-ss11.q11) %>%
  rename(type = ss9.q9) %>% 
  mutate(question = recode(question, ss9.pct9 = "Before", ss11.pct11 = "After"))


ss911graph <- ss911df %>%
  mutate(question = factor(question, levels = c("Before", "After"))) %>%
  ggplot(aes(x = type, fill = question, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  scale_fill_manual(values = c("#666666", "#999999"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = beforeafter) +
  labs(x = '', y = 'Percent') +
  theme_bw() +
  #ggtitle("Opinion about MPAs Before and After Volunteering with CCFRP") +
  theme(panel.grid = element_blank(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r beforeafter_eb plot, fig.height= 7, fig.width= 9, fig.align= "center", echo = F}

ss911graph

```


```{r beforeafter_diff setup, echo = F}

ss9dif <- survey_dat_clean %>% select(q9) %>% drop_na() %>% count(option9 = factor(q9))%>% 
    mutate(pct9 = n/sum(n)*100,
           pct9 = round(pct9, digits = 0)) %>%
  select(option9, pct9)

ss11dif <- survey_dat_clean %>% select(q11) %>% drop_na() %>% 
  count(option11 = factor(q11))%>% 
    mutate(pct11 = n/sum(n)*100,
           pct11 = round(pct11, digits = 0)) %>%
  select(option11, pct11)

ss911dif <- bind_cols(ss9dif, ss11dif) %>%
  mutate(per_dif = pct11-pct9) %>%
  ggplot(aes(x = option9, y = per_dif, label = paste0(per_dif, "%"))) +
  geom_col(position = "dodge")+
  geom_text(aes(y = per_dif + 2 * sign(per_dif)), position = position_dodge(width = 0.9),
            size = 4) +
  geom_hline(yintercept = 0)+
  scale_y_continuous(limits = c(-30,30)) +
  scale_x_discrete(labels = beforeafter) +
  labs(y = 'Percent', x ="", 
       title = "Percent Change in Opinion After Volunteering with CCFRP") +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```


```{r beforeafter_diff plot, fig.height= 7, fig.width= 9, fig.align= "center", echo = F}

ss911dif

```

### 10 & 12

**Before and After** volunteering with CCFRP, did you believe the creation of MPAs would affect the size/abundance of groundfish inside MPAs?


```{r q1012og setup}

ss10 <- survey_dat_clean %>% 
  select(q10) %>% 
  drop_na() %>%
  separate_rows(q10) %>% 
  count(q10 = factor(q10))%>% 
  mutate(pct10 = n/sum(!is.na(survey_dat_clean$q10))*100,
         pct10 = round(pct10, digits = 1))


ss12 <- survey_dat_clean %>% 
  select(q12) %>% 
  drop_na() %>%
  separate_rows(q12) %>% 
  count(q12 = factor(q12))%>% 
  mutate(pct12 = n/sum(!is.na(survey_dat_clean$q12))*100,
         pct12 = round(pct12, digits = 1))

ss1012df = data.frame(ss10$q10, ss10$pct10, ss12$q12, ss12$pct12) %>% pivot_longer(cols=c('ss10.pct10', 'ss12.pct12'), names_to='question', values_to="pct") %>% mutate(question=as.factor(question),ss10.q10 = as.factor(ss10.q10)) %>% select(-ss12.q12) %>% rename(type = ss10.q10) %>% mutate(question = recode(question, ss10.pct10 = "Before", ss12.pct12 = "After"))

beforeafter_groundfish <- c("Increase \nSize", "Increase \nAbundance", "Decrease \nSize",
                            "Decrease \nAbundance", "No Effect \nSize",
                            "No Effect \nAbundance", "I don\'t \nknow", "No \nOpinion")

ss1012graph <- ss1012df %>%
  mutate(question = factor(question, levels = c("Before", "After"))) %>%
  ggplot(aes(x = type, fill = question, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  scale_fill_manual(values = c("#666666", "#999999"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete( labels = beforeafter_groundfish) +
  labs(x = "", y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        axis.title=element_text(size=12),
        legend.title = element_blank(),
        axis.text = element_text(size = 12))

```

```{r , fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss1012graph

```

```{r 1012 setup, echo = F}

ss10fac <- survey_dat_clean %>% 
  select(q10) %>% 
  drop_na() %>%
  separate_rows(q10) %>% 
  count(q10 = factor(q10))%>% 
  mutate(pct10 = n/sum(!is.na(survey_dat_clean$q10))*100,
         pct10 = round(pct10, digits = 1))


ss12fac <- survey_dat_clean %>% 
  select(q12) %>% 
  drop_na() %>%
  separate_rows(q12) %>% 
  count(q12 = factor(q12))%>% 
  mutate(pct12 = n/sum(!is.na(survey_dat_clean$q12))*100,
         pct12 = round(pct12, digits = 1))

ss1012fac = (ss12fac$pct12 - ss10fac$pct10)

dfnew = ss12fac %>% add_column(change = ss1012fac)


ss1012change <- dfnew %>% 
  ggplot(aes(x = q12, y = change, label = paste0(change, "%")))+
  geom_col(position = "dodge")+
  geom_text(aes(y = change + 2 * sign(change)), position = position_dodge(width = 0.9),
            size = 4) +
  geom_hline(yintercept = 0)+
  scale_y_continuous(limits = c(-15,15)) +
  scale_x_discrete(labels = beforeafter_groundfish)+
  labs(y = 'Percent', x ="",
       title = "Percent change in opinion after volunteering with CCFRP") +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```


```{r q1012 plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss1012change

```

### 13

If you believe that California MPA creation affected **groundfish abundance and/or size**, what aspect(s) of MPAs do you believe caused these changes?

```{r q13 setup, echo = F}

mpa_aspects <- c("Location", "Size", "Enforcement", "Network", "Fish population \nprotection", "Voluntary \ncompliance", "Other", "I do not \nbelieve there \nis an effect")

ss13 <- survey_dat_clean %>% 
  select(q13) %>% 
  drop_na() %>%
  separate_rows(q13) %>% 
  count(q13 = factor(q13))%>% 
  mutate(pct = n/sum(!is.na(survey_dat_clean$q13))*100,
         pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q13, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,90)) +
  scale_x_discrete(labels = mpa_aspects) +
  #labs(x = '\nWhat aspects of MPAs affected groundfish size/abundance?', y = 'Percent') +
  labs(x = '', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r q13 plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss13

```


### 14

In your **opinion**, what is the purpose of a Marine Protected Area? 

```{r q14 setup, echo = F}

mpa_purpose <- c("Conserve, restore, \nand understand \nnatural biodiversity \nand ecology", "Provide opportunity \nto experience \nthese areas ", "Restrict industrial \nuses", "Prevent overfishing\n/overuse/degredation", "No purpose", "No opinion")

ss14 <- survey_dat_clean %>% 
  select(q14) %>% 
  drop_na() %>%
  separate_rows(q14) %>% 
  count(q14 = factor(q14))%>% 
  mutate(pct = n/sum(!is.na(survey_dat_clean$q14))*100,
         pct = round(pct, digits = 1))%>%
  ggplot(aes(x = q14, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,90)) +
  scale_x_discrete(labels = mpa_purpose) +
  #labs(x = '\nWhat is the purpose of an MPA?', y = 'Percent') +
  labs(x = "", y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 11))

```

```{r q14 plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss14

```

### 15

Have you ever fished in a Marine Protected Area before it was protected **OR** while volunteering with CCFRP? (If no, skip to section 3)

```{r fished mpa setup, echo = F}

yesno <- c("Yes", "No")

ss15 <- survey_dat_clean %>% select(q15) %>% drop_na() %>% count(q15 = factor(q15))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q15, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = yesno) +
  #labs(x = 'Have You Fished in an MPA?', y = 'Percent') +
  labs(x = '', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r fished mpa plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss15

```


### 16

Think about this when answering a-c: Have you experienced a difference in fishing in an MPA versus outside of an MPA? 

a.  I catch more fish when fishing inside...

b. I catch a greater diversity of fish species when fishing inside...

c. I catch larger fish when I fish inside...


```{r fishingarea setup, echo = F}

## answer option list
fishingarea <- c('MPAs', 'Open to Fishing', 'Don\'t Know', 'No Difference')

ss16a <- survey_dat_clean %>% select(q16) %>% drop_na() %>% count(q16 = factor(q16))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q16, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nHigher Abundance', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss16b <- survey_dat_clean %>% select(q17) %>% drop_na() %>% count(q17 = factor(q17))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q17, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nGreater Diversity', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss16c <- survey_dat_clean %>% select(q18) %>% drop_na() %>% count(q18 = factor(q18))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q18, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nLarger Size', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))
```

```{r fishingarea plot, fig.height= 8, fig.width= 9, fig.align= "center", echo = F}

ss16a/ss16b/ss16c

```


### 17

What is the **primary** reason you enjoy fishing with CCFRP in an MPA? 

```{r primary reason setup, echo = F}

prime_reason <- c("No preference \nfor MPA", "Larger Fish", "More Fish", "More Species", "Collect Scientific \nFishing Data")
## question 17 is q19

ss17 <- survey_dat_clean %>% select(q19) %>% drop_na() %>% count(q19 = factor(q19))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q19, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = prime_reason) +
  #labs(x = '\nWhat is the primary reason you enjoy MPA fishing with CCFRP?', y = 'Percent') +
  labs(x = '', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r primary reason plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss17


```



### 18

Hypothetically, how much would you be willing to pay for one day of catch and release fishing inside an MPA while **NOT** participating on a CCFRP trip?

```{r mpamoney setup, echo = F, eval = F}

money <- c('$0', '$1 - $20', '$21 - $50', '$51 - 100', '$101 - $500', '>$500')

ss18 <- survey_dat_clean %>% select(q20) %>% drop_na() %>% count(q20 = factor(q20))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q20, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,50)) +
  scale_x_discrete(labels = money) +
  #labs(x = '\nHow Much Would You Pay to Fish in an MPA?', y = '\nPercent') +
  labs(x = '', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))



```

```{r mpamoney plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F, eval = F}

ss18

```

## Section 3) Natural Resource Conservation

### 19

In general, would you say you are more conservation-minded or less conservation-minded than others in the recreational angling community?

Compared to the rest of the angling community, I am...

```{r moreless cons setup, echo = F}

moreless <- c("More", "Less", "Similar", "I don\'t know")
## question 19 is q22

ss19 <- survey_dat_clean %>% select(q22) %>% drop_na() %>% count(q22 = factor(q22))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q22, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = moreless) +
  labs(x = '', y = 'Percent') +
  #labs(x = '\nAre you more or less conservation-minded than others?', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```


```{r moreless cons plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss19


```

### 20

Do you participate in activities with conservation-oriented groups (separate from CCFRP)?

```{r conservation group setup, echo = F}


## question 20 is q23

ss20 <- survey_dat_clean %>% select(q23) %>% drop_na() %>% count(q23 = factor(q23))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q23, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = yesno) +
  labs(x = "", y = "Percent")+
  #labs(x = '\nDo you participate with other conservation-oriented groups?', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r conservation group plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss20


```

### 21

How informed do you consider yourself to be concerning ocean issues in California?

```{r informed setup, echo = F}

inform = c("Not well", "Somewhat", "Well", "Very Well", "Unsure")

ss21 <- survey_dat_clean %>% select(q24) %>% drop_na() %>% count(q24 = factor(q24))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q24, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,45)) +
  scale_x_discrete(labels = inform) +
  #labs(x = '\nHow informed do you consider yourself to be concerning ocean issues in Califronia?', y = 'Percent') +
  labs(x = '', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))


```

```{r informed plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss21


```


### 22

In what ways do you currently obtain information about ocean related issues? Select all that apply.


```{r info setup, echo = F}

## Question 22 is q25
info <- c("CCFRP \nrelated events", "Newspaper", "Magazine", "Family\n/friends", "Radio", "Internet", "Social \nmedia", "Television", "Other", "I have not \nsought out \ninformation on \nocean-related \nissues")

ss22 <- survey_dat_clean %>% 
  select(q25) %>% 
  drop_na() %>%
  separate_rows(q25) %>% 
  count(q25 = factor(q25))%>% 
  mutate(pct = n/sum(!is.na(survey_dat_clean$q25))*100,
         pct = round(pct, digits = 1))%>%
  ggplot(aes(x = q25, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,90)) +
  scale_x_discrete(labels = info) +
  #labs(x = '\nWhere do you obtain information about ocean-related issues?', y = 'Percent') +
  labs(x = '', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 11))

```

```{r info plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss22

```

### 23

In your opinion, how well are California groundfish stocks managed? 

I believe California groundfish stocks are:

```{r management setup, echo = F}
## question 23 is q26
managed <- c('Very Well', 'Well', 'Adequately', 'Poorly', 'Very Poorly', 'Not Managed', 'Don\'t Know')

ss23 <- survey_dat_clean %>% select(q26) %>% drop_na() %>% count(q26 = factor(q26))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q26, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,50)) +
  scale_x_discrete(labels = managed) +
  #labs(x = '\nHow Well Managed are California Fisheries?', y = '\nPercent') +
  labs(x = '', y = '\nPercent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r management plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss23

```

### 24

Please rank the following types of fishing gear or fishing practices(from 1 to 8) as having the greatest impact on the degradation of the marine environment or reduction in fish stocks. (1 is least impact and 8 is greatest impact). 


```{r gear type rate set up, echo = F}

# gear <- c("Traps or pots", "Hook & line, \nrecreational", "Bottom \ntrawling",
#           "Longline", "Gill nets", "Midwater \ntrawling", 
#           "Hook & line, \ncommercial", "Spearfishing")

ss24 <- survey_dat_clean%>%
  select(q27_1:q27_8) %>%
  pivot_longer(cols = q27_1:q27_8, names_to = "gear_type") %>%
  mutate(value = as.numeric(value))%>%
  group_by(gear_type)%>%
  summarize(mean = mean(value, na.rm = T),
            mean = round(mean, digits = 2),
            mean_lbl = format(round(mean, digits = 2), nsmall = 2),
            se = std.error(value),
            sd = sd(value, na.rm = T)) %>%
  mutate(gearname = case_when(
    gear_type == "q27_1" ~ "Traps \nor pots",
    gear_type == "q27_2" ~ "Hook & line, \nrecreational",
    gear_type == "q27_3" ~ "Bottom \ntrawling",
    gear_type == "q27_4" ~ "Longline",
    gear_type == "q27_5" ~ "Gill nets",
    gear_type == "q27_6" ~ "Midwater \ntrawling",
    gear_type == "q27_7" ~ "Hook & line, \ncommercial",
    gear_type == "q27_8" ~ "Spearfishing",
  )) %>%
  ggplot(aes(x = reorder(gearname, -mean, sum), 
                           y = mean, label = mean_lbl))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge2(width = 0.9),
            vjust = 0.0,
            hjust = -1.2,
            size = 4)+
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2)+
  scale_y_continuous(limits = c(0, 8), breaks = c(0:8))+
  scale_x_discrete(limits = rev)+
  labs(x = "Gear Type \n", y = "Mean Impact Score")+
  coord_flip()+
  theme_bw()+
  theme(panel.grid = element_blank(),
        legend.position = "none",
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 12))

```


```{r gear type rate plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss24

```

### 25

This question consists of a chart that queries you on your opinion of potential ocean issues. Statements are rated 1-7. An answer of ‘1’ indicates that you strongly disagree, ‘4’ indicates no opinion, and ‘7’ indicates you strongly agree with the statement.

```{r ocean issues setup, echo = F}

ss25 <- survey_dat_clean %>%
  select(q28_1:q28_9) %>%
  pivot_longer(cols = q28_1:q28_9, names_to = "oc_issue") %>%
  mutate(value = as.numeric(value),
         ocean_issue = case_when(
    oc_issue == "q28_1" ~ "Water \nPollution",
    oc_issue == "q28_2" ~ "Marine \nDebris",
    oc_issue == "q28_3" ~ "Loss of \nMarine Biodiversity",
    oc_issue == "q28_4" ~ "Overfishing",
    oc_issue == "q28_5" ~ "Invasive/Exotic \nSpecies",
    oc_issue == "q28_6" ~ "Rising Sea \nTemperatures",
    oc_issue == "q28_7" ~ "Ocean Acidification \nand Hypoxia",
    oc_issue == "q28_8" ~ "Wave energy/ \nPower development",
    oc_issue == "q28_9" ~ "Oil/gas exploration \nor transport"),
    opinion = case_when(
      value == 1 ~ "Strongly Disagree",
      value == 2 ~ "Disagree",
      value == 3 ~ "Somewhat Disagree",
      value == 4 ~ "No Opinion",
      value == 5 ~ "Somewhat Agree",
      value == 6 ~ "Agree",
      value == 7 ~ "Strongly Agree",
    )) %>%
  mutate(opinion = factor(opinion, levels = c("Strongly Disagree", "Disagree", "Somewhat Disagree", "No Opinion", "Somewhat Agree", "Agree", "Strongly Agree"))) %>%
  drop_na() %>%
  ggplot( aes(x = ocean_issue, y = value, fill = opinion))+
  geom_bar(position = "fill", stat = "identity")+
  labs(y = "Percent", x = "Potential Ocean Issue")+
  scale_fill_brewer(palette = "BrBG")+
  coord_flip()+
  theme_bw()+
  theme(panel.grid = element_blank())

```

```{r ocean issues plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss25

```


### 26

How interconnected are you with nature? (1 - 7, where 1 is completely separated and 7 is completely interconnected)

```{r interconnected setup, echo = F}


f = (survey_dat_clean$q39)
survey_dat_clean$q39 = factor(survey_dat_clean$q39, levels = c(1, 2, 3, 4, 5, 6, 7))


ss26 <- survey_dat_clean %>% select(q39) %>% 
  drop_na() %>% 
  count(q39 = factor(q39), drop = FALSE)%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 1), drop = FALSE)%>%
  mutate(q39=factor(q39))%>%
  ggplot(aes(x = q39, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
 scale_x_discrete(drop = FALSE, labels = c("B", "C", "D", "E", "F", "G")) +
  labs(x = 'How interconnected are you with nature?', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss26.1 = ggdraw(ss26) +
  draw_image("vendiagram.png", scale = .5, y = .3)
```


```{r interconnected plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss26.1

```
