---
title: "CCFRP Survey Basic Figures"
author: "E. Johnston, E. Brauer, G. Waltz, B. Ruttenberg, D. Wendt - Updated by S. Ziegler"
date: "December 2021"
output: 
 prettydoc::html_pretty:
    toc: TRUE
    toc_depth: 3
    theme: architect
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      warning = F,
                      message = F)

```

```{r packages}

library(tidyverse)    ## general
library(here)         ## calling data
library(knitr)        ## general
library(kableExtra)   ## for kable styling
library(patchwork)    ## for combining plots
library(ggsci)        ## for color mixer
library(lemon)        ## for brackets
library(ggpubr)       ## for combining plots & common legend
library(cowplot)      ## plotting images on graph
library(plotrix)      ## standard error function

```

```{r data and cleaning, echo = F}

survey_dat <- read_csv(here("Code/SLZ working folder/2021-12-10CCFRP Angler Survey.csv"))

survey_dat <- survey_dat[-c(1:2),]
##351 responses

names(survey_dat) <- tolower(names(survey_dat))

survey_dat_clean <- survey_dat %>%
  filter(finished == 1,
         distributionchannel != "preview") 

survey_dat_clean <- survey_dat_clean %>%
  mutate(unanswered = rowSums(is.na(survey_dat_clean))) %>%
  ## to get rid of the responses where every single question was unanswered.
  filter(unanswered < 55) %>%
  mutate(q1 = as.numeric(q1))

```

## Section 2) Marine Protected Areas

### 9 & 11

**Before and After** volunteering with CCFRP, what was your general opinion of the creation of MPAs in California? My general opinion or MPA creation was ...

```{r beforeafter_eb setup, echo = F}

beforeafter <- c('Positive', 'Somewhat \npositive', 'Neutral', 'Somewhat \nnegative', 'Negative', 'No opinion')

ss9 <- survey_dat_clean %>% select(q9) %>% drop_na() %>% 
  count(q9 = factor(q9))%>% 
  mutate(pct9 = n/sum(n)*100,
         pct9 = round(pct9, digits = 0))

ss11 <- survey_dat_clean %>% select(q11) %>% drop_na() %>% 
  count(q11 = factor(q11)) %>%
  mutate(pct11 = n/sum(n)*100,
         pct11 = round(pct11, digits = 0))

ss911df <- data.frame(ss9$q9, ss9$pct9, ss11$q11, ss11$pct11) %>%
  pivot_longer(cols=c('ss9.pct9', 'ss11.pct11'), names_to='question', values_to="pct") %>%
  mutate(question=as.factor(question), ss9.q9 = as.factor(ss9.q9)) %>% select(-ss11.q11) %>%
  rename(type = ss9.q9) %>% 
  mutate(question = recode(question, ss9.pct9 = "Before", ss11.pct11 = "After"))


ss911graph <- ss911df %>%
  mutate(question = factor(question, levels = c("Before", "After"))) %>%
  ggplot(aes(x = type, fill = question, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge", color="black")+
  scale_fill_manual(values = c("#e0e0e0", "#1a1a1a"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = beforeafter) +
  labs(x = '', y = 'Percent\n') +
  theme_bw() +
  #ggtitle("Opinion about MPAs Before and After Volunteering with CCFRP") +
  theme(panel.grid = element_blank(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

fig1cap <- "Figure 1. The percentage distribution of respondents’ opinions about the creation of MPAs in California before (dark shaded bars, n = 229) and after volunteering with the California Collaborative Fisheries Research Program (light shaded bars, n = 228).Involvement with CCFRP generally corresponded with an increase in positive feelings about the creation of MPAs in California."

```

```{r beforeafter_eb plot, fig.cap = paste(fig1cap), fig.height= 7, fig.width= 9, fig.align= "center", echo = F}

ss911graph

```



```{r beforeafter_diff setup, echo = F}

beforeafter_rev <- c('No opinion', 'Negative', 'Somewhat \nnegative','Neutral', 'Somewhat \npositive','Positive'  )

ss9dif <- survey_dat_clean %>% select(q9) %>% drop_na() %>% count(option9 = factor(q9))%>% 
    mutate(pct9 = n/sum(n)*100,
           pct9 = round(pct9, digits = 0)) %>%
  select(option9, pct9)

ss11dif <- survey_dat_clean %>% select(q11) %>% drop_na() %>% 
  count(option11 = factor(q11))%>% 
    mutate(pct11 = n/sum(n)*100,
           pct11 = round(pct11, digits = 0)) %>%
  select(option11, pct11)

ss911dif <- bind_cols(ss9dif, ss11dif)%>%
  mutate(per_dif = pct11-pct9) %>%
  ggplot(aes(x = option9, y = per_dif, label = paste0(per_dif, "%"))) +
  geom_col(position = "dodge")+
  geom_text(aes(y = per_dif + 2 * sign(per_dif)), position = position_dodge(width = 0.9),
            size = 4) +
  geom_hline(yintercept = 0)+
  scale_y_continuous(limits = c(-30,30), breaks = c(-30, -20, -10, 0, 10, 20, 30)) +
  scale_x_discrete(limits = rev, labels = beforeafter_rev) +
  labs(y = 'Percent\n', x ="", 
       title = "Percent Change in Opinion After Volunteering with CCFRP") +
  coord_flip()+
  theme_bw() + 
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))


fig2cap <- "Figure 2. The percent change in survey respondents’ opinion of California MPAs after volunteering with the California Collaborative Fisheries Research Program (CCFRP), relative to before volunteering with CCFRP (n = 228). There were increases in positive opinions of California MPA’s after involvement with CCFRP, relative to before involvement with CCFRP. All other opinion changes were negative."

```




```{r beforeafter_diff plot, fig.cap = paste(fig2cap), fig.height= 7, fig.width= 9, fig.align= "center", echo = F}

ss911dif

```


```{r 9 11 samp size, eval = F, echo=F}

n9 <- survey_dat_clean %>% select(q9) %>% drop_na()


n11 <- survey_dat_clean %>% select(q11) %>% drop_na() 


```


### 10 & 12

**Before and After** volunteering with CCFRP, did you believe the creation of MPAs would affect the size/abundance of groundfish inside MPAs?


```{r q1012og setup}

ss10 <- survey_dat_clean %>% 
  select(q10) %>% 
  drop_na() %>%
  separate_rows(q10) %>% 
  count(q10 = factor(q10))%>% 
  mutate(pct10 = n/sum(!is.na(survey_dat_clean$q10))*100,
         pct10 = round(pct10, digits = 1))


ss12 <- survey_dat_clean %>% 
  select(q12) %>% 
  drop_na() %>%
  separate_rows(q12) %>% 
  count(q12 = factor(q12))%>% 
  mutate(pct12 = n/sum(!is.na(survey_dat_clean$q12))*100,
         pct12 = round(pct12, digits = 1))

ss1012df = data.frame(ss10$q10, ss10$pct10, ss12$q12, ss12$pct12) %>% pivot_longer(cols=c('ss10.pct10', 'ss12.pct12'), names_to='question', values_to="pct") %>% mutate(question=as.factor(question),ss10.q10 = as.factor(ss10.q10)) %>% select(-ss12.q12) %>% rename(type = ss10.q10) %>% mutate(question = recode(question, ss10.pct10 = "Before", ss12.pct12 = "After"))

beforeafter_groundfish <- c("Increase \nSize", "Increase \nAbundance", "Decrease \nSize",
                            "Decrease \nAbundance", "No Effect \nSize",
                            "No Effect \nAbundance", "I don\'t \nknow", "No \nOpinion")


ss1012graph <- ss1012df %>%
  mutate(question = factor(question, levels = c("Before", "After"))) %>%
  ggplot(aes(x = type, fill = question, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge", color="black")+
  scale_fill_manual(values = c("#e0e0e0", "#1a1a1a"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete( labels = beforeafter_groundfish) +
  labs(x = "", y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        axis.title=element_text(size=12),
        legend.title = element_blank(),
        axis.text = element_text(size = 12))

```

```{r , fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss1012graph

```

```{r 1012 setup, echo = F}

ba_groundfish_rev <- c("No Opinion", "I don\'t know", "No Effect \nAbundance", "No Effect \nSize", "Decrease \nAbundance", "Decrease \nSize", "Increase \nAbundance","Increase \nSize")


ss10fac <- survey_dat_clean %>% 
  select(q10) %>% 
  drop_na() %>%
  separate_rows(q10) %>% 
  count(q10 = factor(q10))%>% 
  mutate(pct10 = n/sum(!is.na(survey_dat_clean$q10))*100,
         pct10 = round(pct10, digits = 1))


ss12fac <- survey_dat_clean %>% 
  select(q12) %>% 
  drop_na() %>%
  separate_rows(q12) %>% 
  count(q12 = factor(q12))%>% 
  mutate(pct12 = n/sum(!is.na(survey_dat_clean$q12))*100,
         pct12 = round(pct12, digits = 1))

ss1012fac = (ss12fac$pct12 - ss10fac$pct10)

dfnew = ss12fac %>% add_column(change = ss1012fac)


ss1012change <- dfnew %>% 
  ggplot(aes(x = q12, y = change, label = paste0(change, "%")))+
  geom_col(position = "dodge")+
  geom_text(aes(y = change + 2 * sign(change)), position = position_dodge(width = 0.9),
            size = 4) +
  geom_hline(yintercept = 0)+
  scale_y_continuous(limits = c(-20,20)) +
  scale_x_discrete(limits = rev, labels = ba_groundfish_rev)+
  labs(y = 'Percent\n', x ="",
       title = "Percent change in opinion after volunteering with CCFRP") +
  coord_flip()+
  theme_bw() + 
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```


```{r q1012 plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss1012change

```

### 13

If you believe that California MPA creation affected **groundfish abundance and/or size**, what aspect(s) of MPAs do you believe caused these changes?

```{r q13 setup, echo = F}

mpa_aspects <- c("Location", "Size", "Enforcement", "Network", "Fish population \nprotection", "Voluntary \ncompliance", "Other", "I do not \nbelieve there \nis an effect")

ss13 <- survey_dat_clean %>% 
  select(q13) %>% 
  drop_na() %>%
  separate_rows(q13) %>% 
  count(q13 = factor(q13))%>% 
  mutate(pct = n/sum(!is.na(survey_dat_clean$q13))*100,
         pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q13, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,90)) +
  scale_x_discrete(labels = mpa_aspects) +
  #labs(x = '\nWhat aspects of MPAs affected groundfish size/abundance?', y = 'Percent') +
  labs(x = '', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r q13 plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss13

```


### 14

In your **opinion**, what is the purpose of a Marine Protected Area? 

```{r q14 setup, echo = F}

mpa_purpose <- c("Conserve, restore, \nand understand \nnatural biodiversity \nand ecology", "Provide opportunity \nto experience \nthese areas ", "Restrict industrial \nuses", "Prevent overfishing\n/overuse/degredation", "No purpose", "No opinion")

ss14 <- survey_dat_clean %>% 
  select(q14) %>% 
  drop_na() %>%
  separate_rows(q14) %>% 
  count(q14 = factor(q14))%>% 
  mutate(pct = n/sum(!is.na(survey_dat_clean$q14))*100,
         pct = round(pct, digits = 1))%>%
  ggplot(aes(x = q14, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,90)) +
  scale_x_discrete(labels = mpa_purpose) +
  #labs(x = '\nWhat is the purpose of an MPA?', y = 'Percent') +
  labs(x = "", y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 11))

```

```{r q14 plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss14

```

### 15

Have you ever fished in a Marine Protected Area before it was protected **OR** while volunteering with CCFRP? (If no, skip to section 3)

```{r fished mpa setup, echo = F}

yesno <- c("Yes", "No")

ss15 <- survey_dat_clean %>% select(q15) %>% drop_na() %>% count(q15 = factor(q15))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q15, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = yesno) +
  #labs(x = 'Have You Fished in an MPA?', y = 'Percent') +
  labs(x = '', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r fished mpa plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss15

```


### 16

Think about this when answering a-c: Have you experienced a difference in fishing in an MPA versus outside of an MPA? 

a.  I catch more fish when fishing inside...

b. I catch a greater diversity of fish species when fishing inside...

c. I catch larger fish when I fish inside...


```{r fishingarea setup, echo = F}

## answer option list
fishingarea <- c('MPAs', 'Open to Fishing', 'Don\'t Know', 'No Difference')

ss16a <- survey_dat_clean %>% select(q16) %>% drop_na() %>% count(q16 = factor(q16))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q16, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nHigher Abundance', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss16b <- survey_dat_clean %>% select(q17) %>% drop_na() %>% count(q17 = factor(q17))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q17, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nGreater Diversity', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss16c <- survey_dat_clean %>% select(q18) %>% drop_na() %>% count(q18 = factor(q18))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q18, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nLarger Size', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))
```

```{r fishingarea plot, fig.height= 8, fig.width= 9, fig.align= "center", echo = F, eval = F}

ss16a/ss16b/ss16c

```


```{r 16combo setup, echo = F}

ss16a2 <- survey_dat_clean %>% select(q16) %>% drop_na() %>% count(q = factor(q16))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0),
           Difference = "Higher Abundance")
ss16b2 <- survey_dat_clean %>% select(q17) %>% drop_na() %>% count(q = factor(q17))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0),
           Difference = "Greater Diversity")
ss16c2 <- survey_dat_clean %>% select(q18) %>% drop_na() %>% count(q = factor(q18))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0),
           Difference = "Larger Size")

ss16com <- bind_rows(ss16a2, ss16b2, ss16c2) %>%
  mutate(Difference = factor(Difference, levels = c("Higher Abundance", "Larger Size",
                                                    "Greater Diversity")))

ss16plot <- ggplot(data = ss16com, aes(x = q, y = pct, fill = Difference, 
                                       label = paste0(pct, "%")))+
  geom_col(position = "dodge", color="black")+
  #scale_fill_npg()+
  ## for greyscale below
  scale_fill_manual(values = c("#ffffff",  "#bababa", "#1a1a1a"))+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5, size = 4)+
  scale_y_continuous(limits = c(0,85)) +
  scale_x_discrete(labels = fishingarea) +
  labs(x = '\nLarger Size', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))



```

```{r 16combo plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss16plot

```

### 17

What is the **primary** reason you enjoy fishing with CCFRP in an MPA? 

```{r primary reason setup, echo = F}

prime_reason <- c("No preference \nfor MPA", "Larger Fish", "More Fish", "More Species", "Collect Scientific \nFishing Data")
## question 17 is q19

ss17 <- survey_dat_clean %>% select(q19) %>% drop_na() %>% count(q19 = factor(q19))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q19, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = prime_reason) +
  #labs(x = '\nWhat is the primary reason you enjoy MPA fishing with CCFRP?', y = 'Percent') +
  labs(x = '', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r primary reason plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F, eval = F}

ss17


```

   > **62%** of CCFRP volunteer fishers say that collecting scientific fishing data is the *primary* reason they enjoy fishing with CCFRP in MPAs.

### 18

Hypothetically, how much would you be willing to pay for one day of catch and release fishing inside an MPA while **NOT** participating on a CCFRP trip?

```{r mpamoney setup, echo = F, eval = F}

money <- c('$0', '$1 - $20', '$21 - $50', '$51 - 100', '$101 - $500', '>$500')

ss18 <- survey_dat_clean %>% select(q20) %>% drop_na() %>% count(q20 = factor(q20))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q20, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,50)) +
  scale_x_discrete(labels = money) +
  #labs(x = '\nHow Much Would You Pay to Fish in an MPA?', y = '\nPercent') +
  labs(x = '', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))



```

```{r mpamoney plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F, eval = F}

ss18

```

  > **1/3** of CCFRP volunteer fishers would pay between *$50 and $500* for a day of catch-and-release fishing in an MPA.

## Section 3) Natural Resource Conservation

### 19

In general, would you say you are more conservation-minded or less conservation-minded than others in the recreational angling community?

Compared to the rest of the angling community, I am...

```{r moreless cons setup, echo = F}

moreless <- c("More", "Less", "Similar", "I don\'t know")
## question 19 is q22

ss19 <- survey_dat_clean %>% select(q22) %>% drop_na() %>% count(q22 = factor(q22))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q22, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = moreless) +
  labs(x = '', y = 'Percent\n') +
  #labs(x = '\nAre you more or less conservation-minded than others?', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```


```{r moreless cons plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss19


```

### 20

Do you participate in activities with conservation-oriented groups (separate from CCFRP)?

```{r conservation group setup, echo = F}

yesno <- c("Yes", "No")

## question 20 is q23

ss20 <- survey_dat_clean %>% select(q23) %>% drop_na() %>% count(q23 = factor(q23))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q23, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
  scale_x_discrete(labels = yesno) +
  labs(x = "", y = "Percent\n")+
  #labs(x = '\nDo you participate with other conservation-oriented groups?', y = 'Percent') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r conservation group plot, fig.height= 6, fig.width= 9, fig.align= "center", eval = F, echo = F}

ss20


```

  > **55%** of CCFRP volunteer fishers participate in activities with other conservation-oriented groups; **45%** of CCFRP volunteer fishers do not.

### 21

How informed do you consider yourself to be concerning ocean issues in California?

```{r informed setup, echo = F}

inform = c("Not well", "Somewhat", "Well", "Very Well", "Unsure")

ss21 <- survey_dat_clean %>% select(q24) %>% drop_na() %>% count(q24 = factor(q24))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q24, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,45)) +
  scale_x_discrete(labels = inform) +
  #labs(x = '\nHow informed do you consider yourself to be concerning ocean issues in Califronia?', y = 'Percent') +
  labs(x = '', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))


```

```{r informed plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss21


```


### 22

In what ways do you currently obtain information about ocean related issues? Select all that apply.


```{r info setup, echo = F}

## Question 22 is q25
info <- c("CCFRP \nrelated events", "Newspaper", "Magazine", "Family\n/friends", "Radio", "Internet", "Social \nmedia", "Television", "Other", "I have not \nsought out \ninformation on \nocean-related \nissues")

ss22 <- survey_dat_clean %>% 
  select(q25) %>% 
  drop_na() %>%
  separate_rows(q25) %>% 
  count(q25 = factor(q25))%>% 
  mutate(pct = n/sum(!is.na(survey_dat_clean$q25))*100,
         pct = round(pct, digits = 1))%>%
  ggplot(aes(x = q25, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,90)) +
  scale_x_discrete(labels = info) +
  #labs(x = '\nWhere do you obtain information about ocean-related issues?', y = 'Percent') +
  labs(x = '', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 11))

```

```{r info plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss22

```

### 23

In your opinion, how well are California groundfish stocks managed? 

I believe California groundfish stocks are:

```{r management setup, echo = F}
## question 23 is q26
managed <- c('Very Well', 'Well', 'Adequately', 'Poorly', 'Very Poorly', 'Not Managed', 'Don\'t Know')

ss23 <- survey_dat_clean %>% select(q26) %>% drop_na() %>% count(q26 = factor(q26))%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 0))%>%
  ggplot(aes(x = q26, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,50)) +
  scale_x_discrete(labels = managed) +
  #labs(x = '\nHow Well Managed are California Fisheries?', y = '\nPercent') +
  labs(x = '', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

```

```{r management plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss23

```

### 24

Please rank the following types of fishing gear or fishing practices(from 1 to 8) as having the greatest impact on the degradation of the marine environment or reduction in fish stocks. (1 is least impact and 8 is greatest impact). 


```{r gear type rate set up, echo = F}

# gear <- c("Traps or pots", "Hook & line, \nrecreational", "Bottom \ntrawling",
#           "Longline", "Gill nets", "Midwater \ntrawling", 
#           "Hook & line, \ncommercial", "Spearfishing")

ss24 <- survey_dat_clean%>%
  select(q27_1:q27_8) %>%
  pivot_longer(cols = q27_1:q27_8, names_to = "gear_type") %>%
  mutate(value = as.numeric(value))%>%
  group_by(gear_type)%>%
  summarize(mean = mean(value, na.rm = T),
            mean = round(mean, digits = 2),
            mean_lbl = format(round(mean, digits = 2), nsmall = 2),
            se = std.error(value),
            sd = sd(value, na.rm = T)) %>%
  mutate(gearname = case_when(
    gear_type == "q27_1" ~ "Traps \nor pots",
    gear_type == "q27_2" ~ "Hook & line, \nrecreational",
    gear_type == "q27_3" ~ "Bottom \ntrawling",
    gear_type == "q27_4" ~ "Longline",
    gear_type == "q27_5" ~ "Gill nets",
    gear_type == "q27_6" ~ "Midwater \ntrawling",
    gear_type == "q27_7" ~ "Hook & line, \ncommercial",
    gear_type == "q27_8" ~ "Spearfishing", )) %>%
  ggplot(aes(x = reorder(gearname, -mean, sum), 
                           y = mean, label = mean_lbl, aes(color=gearname)))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge2(width = 0.9),
            vjust = 0.0,
            hjust = -1.2,
            size = 4)+
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, color=gearname), width = 0.2)+
  scale_y_continuous(limits = c(0, 8), breaks = c(0:8))+
  scale_x_discrete(limits = rev)+
  labs(x = "Gear Type \n", y = "Mean Impact Score")+
  coord_flip()+
  theme_bw()+
  theme(panel.grid = element_blank(),
        legend.position = "none",
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 12))

```


```{r gear type rate plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss24

```

### 25

This question consists of a chart that queries you on your opinion of potential ocean issues. Statements are rated 1-7. An answer of ‘1’ indicates that you strongly disagree, ‘4’ indicates no opinion, and ‘7’ indicates you strongly agree with the statement.

```{r ocean issues setup, echo = F}

ss25 <- survey_dat_clean %>%
  select(q28_1:q28_9) %>%
  pivot_longer(cols = q28_1:q28_9, names_to = "oc_issue") %>%
  mutate(value = as.numeric(value),
         ocean_issue = case_when(
    oc_issue == "q28_1" ~ "Water \nPollution",
    oc_issue == "q28_2" ~ "Marine \nDebris",
    oc_issue == "q28_3" ~ "Loss of \nMarine Biodiversity",
    oc_issue == "q28_4" ~ "Overfishing",
    oc_issue == "q28_5" ~ "Invasive/Exotic \nSpecies",
    oc_issue == "q28_6" ~ "Rising Sea \nTemperatures",
    oc_issue == "q28_7" ~ "Ocean Acidification \nand Hypoxia",
    oc_issue == "q28_8" ~ "Wave energy/ \nPower development",
    oc_issue == "q28_9" ~ "Oil/gas exploration \nor transport"),
    opinion = case_when(
      value == 1 ~ "Strongly Disagree",
      value == 2 ~ "Disagree",
      value == 3 ~ "Somewhat Disagree",
      value == 4 ~ "No Opinion",
      value == 5 ~ "Somewhat Agree",
      value == 6 ~ "Agree",
      value == 7 ~ "Strongly Agree",
    )) %>%
  mutate(opinion = factor(opinion, levels = c("Strongly Disagree", "Disagree", "Somewhat Disagree", "No Opinion", "Somewhat Agree", "Agree", "Strongly Agree"))) %>%
  drop_na() %>%
  ggplot( aes(x = ocean_issue, y = value, fill = opinion))+
  geom_bar(position = "fill", stat = "identity")+
  labs(y = "\nPercent", x = "Potential Ocean Issue\n")+
  scale_fill_brewer(palette = "BrBG")+
  coord_flip()+
  theme_bw()+
  theme(panel.grid = element_blank())

```

```{r ocean issues plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss25

```


### 26

How interconnected are you with nature? (1 - 7, where 1 is completely separated and 7 is completely interconnected)

```{r interconnected setup, echo = F}


f = (survey_dat_clean$q39)
survey_dat_clean$q39 = factor(survey_dat_clean$q39, levels = c(1, 2, 3, 4, 5, 6, 7))


ss26 <- survey_dat_clean %>% select(q39) %>% 
  drop_na() %>% 
  count(q39 = factor(q39), drop = FALSE)%>% 
    mutate(pct = n/sum(n)*100,
           pct = round(pct, digits = 1), drop = FALSE)%>%
  mutate(q39=factor(q39))%>%
  ggplot(aes(x = q39, y = pct, label = paste0(pct, "%")))+
  geom_col(position = "dodge")+
  geom_text(position = position_dodge(width = 0.9),
            vjust = -0.5,
            size = 4)+
  scale_y_continuous(limits = c(0,75)) +
 scale_x_discrete(drop = FALSE, labels = c("B", "C", "D", "E", "F", "G")) +
  labs(x = 'How interconnected are you with nature?', y = 'Percent\n') +
  theme_bw() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

ss26.1 = ggdraw(ss26) +
  draw_image("vendiagram.png", scale = .5, y = .3)
```


```{r interconnected plot, fig.height= 6, fig.width= 9, fig.align= "center", echo = F}

ss26.1

```


Filter out specific demographic information for more complex analyses. 


The percentage distribution of respondents’ opinions about the creation of MPAs in California before or after volunteering with the California Collaborative Fisheries Research Program.

```{r more complex analyses, echo=FALSE}
# question 16a,b,c are q16, q17, q19
# question 23 is q26

survey_dat_filter<-survey_dat_clean%>%
  select(responseid,q1,q2,q3,q4,q30,q9,q10,q11,q12, q13, q16, q17, q18, q26)
#survey_dat_filter$q1 <- recode(survey_dat_filter$q1, 20118 = 2018)
```

Examine the percentage distribution of respondents’ opinions about the creation of MPAs in California before or after volunteering with the California Collaborative Fisheries Research Program by year of initial volunteering

```{r}
beforeafter <- c('Positive', 'Somewhat \npositive', 'Neutral', 'Somewhat \nnegative', 'Negative', 'No opinion')

# Start examining question 9 in relation to the year of initial participation
q9<-survey_dat_filter%>%select(q1, q9)%>%drop_na()%>%
  group_by(q1)%>%
  count(q9 = factor(q9))%>%
  spread(q9, n)

q9[is.na(q9)] <- 0
  
str(q9)

q9<-q9%>%
  gather(q9, n, -q1)%>%
  group_by(q1)%>%
  mutate(pct9 = n/sum(n)*100,
        pct9 = round(pct9, digits = 1))%>%
  filter(q1>=2007 & q1<=2021)

q9$q1<-as.factor(q9$q1)

ggplot(q9, aes(x=q9, y=pct9, fill=q1, label = paste0(pct9, "%")))+
  geom_bar(stat="identity", position=position_dodge(1), color="black")+
  scale_x_discrete(labels = beforeafter)+
   labs(x = '', y = 'Percent\n') +
  theme_bw() +
  geom_text(position = position_dodge(width = 1),
            vjust = -0.5,
            size = 2)+
  ggtitle("Opinion about MPAs Before Volunteering with CCFRP") +
  theme(panel.grid = element_blank(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

# Start examining question 11 in relation to the year of initial participation
q11<-survey_dat_filter%>%select(q1, q11)%>%drop_na()%>%
  group_by(q1)%>%
  count(q11 = factor(q11))%>%
  spread(q11, n)

q11[is.na(q11)] <- 0
  
str(q11)

q11<-q11%>%
  gather(q11, n, -q1)%>%
  group_by(q1)%>%
  mutate(pct11 = n/sum(n)*100,
        pct11 = round(pct11, digits = 1))%>%
   filter(q1>=2007 & q1<=2021)

q11$q1<-as.factor(q11$q1)

ggplot(q11, aes(x=q11, y=pct11, fill=q1, label = paste0(pct11, "%")))+
  geom_bar(stat="identity", position=position_dodge(1), color="black")+
  scale_x_discrete(labels = beforeafter)+
   labs(x = '', y = 'Percent\n') +
  theme_bw() +
  geom_text(position = position_dodge(width = 1),
            vjust = -0.5,
            size = 2)+
  ggtitle("Opinion about MPAs After Volunteering with CCFRP") +
  theme(panel.grid = element_blank(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

q911.1<-left_join(q9, q11 ,by="q1")%>%
  filter(q9==q11)
q911.1$change<-(q911.1$pct11-q911.1$pct9)

ggplot(q911.1, aes(x=q11, y=change, fill=q1, label = paste0(change, "%")))+
  geom_bar(stat="identity", position=position_dodge(1), color="black")+
  scale_x_discrete(labels = beforeafter)+
 # scale_y_continuous(limits = c(0,85))+
  scale_fill_discrete(labels = institution, "Institution")+ 
  labs(x = '', y = 'Percent\n') +
  theme_bw() +
  geom_text(position = position_dodge(width = 1),
            vjust = -0.5,
            size = 2)+
  ggtitle("Change in opinion about MPAs After Volunteering with CCFRP") +
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12),
        legend.position = "none")+
  facet_wrap(~q1)

```

Perception of MPAs Before and After working with CCFRP based on insitution

```{r}
beforeafter <- c('Positive', 'Somewhat \npositive', 'Neutral', 'Somewhat \nnegative', 'Negative', 'No opinion')

institution<- c('Humboldt', "Bodega", "MLML", "Cal Poly", "UCSB", "SIO")
# Start examining question 9 in relation to the year of initial participation
q9.4<-survey_dat_filter%>%select(q4, q9)%>%drop_na()%>%
  group_by(q4)%>%
  count(q9 = factor(q9))%>%
  spread(q9, n)

q9.4[is.na(q9.4)] <- 0
  
str(q9.4)

q9.4<-q9.4%>%
  gather(q9, n, -q4)%>%
  group_by(q4)%>%
  mutate(pct9 = n/sum(n)*100,
        pct9 = round(pct9, digits = 1))

before<-ggplot(q9.4, aes(x=q9, y=pct9, fill=q4, label = paste0(pct9, "%")))+
  geom_bar(stat="identity", position=position_dodge(1), color="black")+
  scale_x_discrete(labels = beforeafter)+
  scale_y_continuous(limits = c(0,85))+
  scale_fill_discrete(labels = institution, "Institution")+
   labs(x = '', y = 'Percent\n') +
  theme_bw() +
  facet_wrap(~q4, labeller=labeller)+
  geom_text(position = position_dodge(width = 1),
            vjust = -0.5,
            size = 2)+
  ggtitle("Opinion about MPAs Before Volunteering with CCFRP") +
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))

# Start examining question 11 in relation to the year of initial participation
q11.4<-survey_dat_filter%>%select(q4, q11)%>%drop_na()%>%
  group_by(q4)%>%
  count(q11 = factor(q11))%>%
  spread(q11, n)

q11.4[is.na(q11.4)] <- 0
  
str(q11.4)

q11.4<-q11.4%>%
  gather(q11, n, -q4)%>%
  group_by(q4)%>%
  mutate(pct11 = n/sum(n)*100,
        pct11 = round(pct11, digits = 1))


after<-ggplot(q11.4, aes(x=q11, y=pct11, fill=q4, label = paste0(pct11, "%")))+
  geom_bar(stat="identity", position=position_dodge(1), color="black")+
  scale_x_discrete(labels = beforeafter)+
  scale_y_continuous(limits = c(0,85))+
  scale_fill_discrete(labels = institution, "Institution")+ 
  labs(x = '', y = 'Percent\n') +
  theme_bw() +
  facet_wrap(~q4, labeller=labeller)+
  geom_text(position = position_dodge(width = 1),
            vjust = -0.5,
            size = 2)+
  ggtitle("Opinion about MPAs After Volunteering with CCFRP") +
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12))


#Group the question 9 and 11 to calculate the % change after working with CCFRP.
q911.4<-left_join(q9.4, q11.4,by="q4")%>%
  filter(q9==q11)
q911.4$change<-(q911.4$pct11-q911.4$pct9)

labeller = labeller(q4 = 
    c('1'='Humboldt', '2'= "Bodega", '3'= "MLML", '4' = "Cal Poly",'5'="UCSB", '6'= "SIO"))
ggplot(q911.4, aes(x=q11, y=change, fill=q4, label = paste0(change, "%")))+
  geom_bar(stat="identity", position=position_dodge(1), color="black")+
  scale_x_discrete(labels = beforeafter)+
 # scale_y_continuous(limits = c(0,85))+
  scale_fill_discrete(labels = institution, "Institution")+ 
  labs(x = '', y = 'Percent\n') +
  theme_bw() +
  geom_text(position = position_dodge(width = 1),
            vjust = -0.5,
            size = 2)+
  ggtitle("Change in opinion about MPAs After Volunteering with CCFRP") +
  theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=12),
        axis.text = element_text(size = 12),
        legend.position = "none")+
  facet_wrap(~q4, labeller=labeller)



xx<-survey_dat_filter%>%select(responseid, q9, q11)%>%drop_na()%>%
  filter(q9!="6" & q11!="6")%>%
  group_by(responseid)
xx$q9<-as.numeric(xx$q9)
xx$q11<-as.numeric(xx$q11)

xx$change<-xx$q9-xx$q11



  group_by(q4)%>%
  count(q9 = factor(q9))%>%
  spread(q9, n)

  
```


